emmeans and varpred comparison

### 2021-10-28 compare_emmeans_varpred.rmd
Categorical interactions

library(shellpipes)
library(glmmTMB)
library(dplyr)
library(ggplot2)
library(vareffects); varefftheme()
library(emmeans)

@@

>>>>

library(shellpipes)
library(glmmTMB)
library(dplyr)
library(ggplot2)
library(vareffects); varefftheme()
library(emmeans)
library(effects)

@@

\section{Dealing with categorical iterations}

```{r categorical_toy, echo=TRUE}
df <- (expand.grid(services=c("water", "garbage", "toilet")
		, gender=c("Male", "Female")
		, statusP=c("Base year", "Not observed", "Unimproved", "Improved")
	)
	%>% mutate(age = rnorm(n())
		, status=rbinom(n(), 1, plogis(rnorm(n(), 3, 5)))
	)
)
head(df)
```

Model:

```{r toy_model, echo=TRUE}
toy_mod <- glm(status~-1+services+(age+gender+statusP):services
	, data=df
	, family="binomial"
	, contrasts=list(services="contr.sum")
)
```

\subsection{varpred}

- Averaging all the columns of model matrix?

```{r varpred_all_av}
varpred_all_av <- varpred(toy_mod, "services", handle.inter="emmeans", returnall=TRUE)
print(varpred_all_av$raw$model.matrix)
```

- On baseline level?

```{r varpred_no_av}
varpred_no_av <- varpred(toy_mod, "services", handle.inter="effects", returnall=TRUE)
print(varpred_no_av$raw$model.matrix)
```

\subsection{emmeans}

```{r emmeans_toy}
emmeans_toy <- emmeans(toy_mod, specs=~services, nesting=NULL, weighting="equal")
print(emmeans_toy@linfct)
```

\subsection{Effects}

```{r effects_toy}
effects_toy <- Effect("services", toy_mod)
print(effects_toy$model.matrix)
```
